Local Spectral Clustering of Density Upper Level Sets

### 2019-11-04 arxiv/local_spectral_density_clustering_arxiv.tex
just testing

\begin{remark}
	We also note that our lower bound is of course specific to the PPR algorithm. As mentioned previously, density clustering is a well-studied problem, and in particular under our assumptions classical plug-in density cluster estimators can consistently recover the $\sigma$-expansion $\Csig$ of a density cluster $\Cset$, even when $\epsilon$ is large compared to $\frac{\sigma}{\rho}$. That PPR has difficulty recovering density clusters which can be easily estimated by standard plug-in approaches is not surprising, nor is it a knock on PPR. Rather, it simply reflects that while classical density clustering approaches are specifically designed to identify high-density regions regardless of their geometry, PPR considers geometry as well as density when deciding upon the optimal cluster.
\end{remark}

>>>>

\begin{remark}
	We also note that our lower bound is of course specific to the PPR algorithm. As mentioned previously, density clustering is a well-studied problem, and in particular under our assumptions classical plug-in density cluster estimators can consistently recover the $\sigma$-expansion $\Csig$ of a density cluster $\Cset$, even when $\epsilon$ is large compared to $\frac{\sigma}{\rho}$ \sbcomment{small?}. That PPR has difficulty recovering density clusters which can be easily estimated by standard plug-in approaches is not surprising, nor is it a knock on PPR. Rather, it simply reflects that while classical density clustering approaches are specifically designed to identify high-density regions regardless of their geometry, PPR considers geometry as well as density when deciding upon the optimal cluster.
\end{remark}
